---
title: "AIS A THON"
output: word_document
date: "2023-04-19"
---

###

Prompt 3: Build a model to predict whether a particular transaction will have an error. 

Solution: Create a descion tree since the y-variable is binary and not necessarily quantitative. Want to predict whether given certain factors might hypothetically lead to a error in a transaction

###

libraries
```{r}
library(datasets)
library(tidyverse) 
library(caret)
library(grid)
library(gridExtra)
library(GGally)
library(rpart)
library(rpart.plot)
library(corrplot)
library(ROCR)
library(readxl)
```

read dataset
```{r}
set1 =read.csv("AIS-A-THON_dataset.csv", header =T, na.strings = "?")
names(set1)
head(set1)
str(set1)
```

###

dictionary:

account_number_sender, account_number_receiver - nominal data fields with account numbers for both parties: senders and receivers of money

transaction_timestamp - field containing the date and time of the transaction

transfer_amount - the total amount being transferred from sender’s account to the receiver’s account

beginning_balance_sender - this field is to inform if the sender had sufficient funds beforehand

bank_sender - categorical field containing the bank which stores the sender’s money

os_sender, os_receiver - type of operating systems that the sender and receiver have on their phones

unanimous_agreement - binary field indicating whether both parties agreed to the transaction

transaction_error - binary field indicating whether the transaction resulted in an error

###


preprocess data
```{r}
set2 <- set1[c(4:10)]   #get rid of irrelevant features
#check structure of dataset
names(set2)
dim(set2)
head(set2)
#convert to factor since they are going to be used as classifiers
set2$transaction_error <- as.factor(set2$transaction_error)
set2$unanimous_agreement <- as.factor(set2$unanimous_agreement)
str(set2)
```

run descion tree model
```{r}
treeFit <- rpart(transaction_error~.,data=set2, method = 'class')
print(treeFit)
```

```{r}
#function to create a visual plot
fig <- function(width, heigth){
     options(repr.plot.width = width, repr.plot.height = heigth)
}
```


visualize the tree
```{r}
fig(20, 20)
rattle::fancyRpartPlot(treeFit, type = 1, sub = "")
```


Train and test data set for accuracy 
```{r}
set.seed(343)

set2[, 'train'] <- ifelse(runif(nrow(set2)) < 0.75, 1, 0)

trainSet <- set2[set2$train == 1,]
testSet <- set2[set2$train == 0, ]

trainColNum <- grep('train', names(trainSet))
trainColNum

trainSet <- trainSet[, -trainColNum]
testSet <- testSet[, -trainColNum]
```

Descision tree for trained set
```{r}
treeFit <- rpart(transaction_error~.,data=trainSet,method = 'class')
print(treeFit)
```

```{r}
rattle::fancyRpartPlot(treeFit, type = 1, sub = "")
```

check accuracy of the tree
```{r}
Prediction1 <- predict(treeFit,newdata=testSet,type = 'class')
confusionMatrix(Prediction1,testSet$transaction_error)
```
Logistic Regression Model
```{r}
model <- glm(transaction_error ~ transfer_amount , 
             data = set2, family = binomial)
summary(model)
plot(model)
```


```{r}
set.seed(343)
trainIndex <- createDataPartition(set2$transaction_error, p = .75, list = FALSE,times = 1)
train <- set2[trainIndex,]
valid <- set2[-trainIndex,]
```


Logistic Regression Model
```{r}
model <- glm(transaction_error ~. , 
             data = train, family = binomial)
summary(model)
plot(model)
```


accuracy 
```{r}
predict_reg <- predict(model, valid, type = 'response')
y_predicted <- ifelse(predict_reg > 0.5, 1, 0)
y_predicted <- as.factor(y_predicted)
str(y_predicted)
table(y_predicted, valid$transaction_error)
accuracy <- table(y_predicted, (valid$transaction_error))
sum(diag(accuracy))/sum(accuracy)
```